Scalar Items in Embedded Position: {A}n Experimental Revisit

### 2012-07-02 text/paper/paper.tex
paper just typos
paper added notes

  \caption{Distinguishing scenarious for \as-sentences}
  \label{fig:AS-distinguishing-pics}
\end{figure}

@@

  \caption{Distinguishing scenarious for \es-sentences}
  \label{fig:ES-distinguishing-pics}

@@

\subsection{Critique}
\label{sec:critique}

Summing up, the mentioned studies have presented diverging evidence
concerning the availability of local readings. Varoius problematic
aspects of these studies have already been discussed elsewhere
\citep[e.g.][]{CliftonDube2010:Embedded-Implic,ChemlaSpector2010:Experimental-Ev,Tielvan-Tiel2012:Embedded-Scalar}. Here,
we want to point out two particular methodological problems that do
impede their interpretation. However, we also want to make clear that
these problems follow almost directly from the nature of the
phenomenon under investigation and therefore seem nearly impossible to
avoid.

@@

>>>>

  \caption{Distinguishing scenarios for \as-sentences}
  \label{fig:AS-distinguishing-pics}
\end{figure}

@@

  \caption{Distinguishing scenarios for \es-sentences}
  \label{fig:ES-distinguishing-pics}

@@

\subsection{Reflection}
\label{sec:critique}

Summing up, the mentioned studies have presented diverging evidence
concerning the availability of local readings. Various problematic
aspects of these studies have already been discussed elsewhere
\citep[e.g.][]{CliftonDube2010:Embedded-Implic,ChemlaSpector2010:Experimental-Ev,Tielvan-Tiel2012:Embedded-Scalar}. Here,
we want to point out two particular methodological problems that do
impede their interpretation. However, we also want to make clear that
these problems follow almost directly from the nature of the
phenomenon under investigation and therefore seem nearly impossible to
avoid.

@@

\bigskip

We also tested examples like (\ref{bsp:EA}), which are the ``global
alternatives'' to \es-sentences, with a universal quantifier where
\es-sentences have scalar \emph{some}.
\begin{exe}
\ex \gll F\"{u}r \mymark{genau} \mymark{eines} dieser Kinder gilt: es mag \mymark{jede} dieser
  Speisen. \label{bsp:EA}\\
  For exactly one {of these} children {it holds} it likes all {of
    these} dishes.\\
  For exactly one of these children it holds that it likes all of these dishes.
\end{exe}
Sentence like (\ref{bsp:EA}) are literally true in both of the
situations given in Figure~\ref{fig:EA-distinguishing-pics}, but these
situations differ in the truth value of the corresponding
\es-sentence. Interestingly, we found a difference in acceptability,
but a curious one. The sentence was judged \emph{true} in 90.34\% of
the cases for the situation in Figure~\ref{fig:global-EA} and in
98.34\% in situation \ref{fig:literal-EA}. The observed difference is
significant ($t = -3.8259$, $df = 322.375$, $p < 0.001$). That is a
curious finding, because, from the point of view of implicature
calculation, the only thing that could plausibly explain this
acceptability difference is the presence of a global implicature,
resulting from the negation of the corresponding \es-sentence. But
such a putative global implicature would be true in the
situation~\ref{fig:global-EA}, but false in the
situation~\ref{fig:literal-EA}. Consequently, the observed difference
in acceptability cannot be explained simply in terms of the hypothesis
of \citet{ChemlaSpector2010:Experimental-Ev} that acceptability is
proportional to the number of available true readings: if a putative
global reading is at stake, the acceptability pattern should be
reversed; if no such global reading is at stake, then the
acceptability difference cannot be explained.

\subfloat[fig:global][global]{
  \label{fig:global-EA}

        \node (table) [right of = X-4] {
          \begin{tabular}{ll}
            \lit & true \\
            \glb & true
          \end{tabular}};

} \qquad \qquad
\subfloat[fig:literal][literal]{
  \label{fig:literal-EA}

        \node (table) [right of = X-4] {
          \begin{tabular}{ll}
            \lit & true \\
            \glb & false
          \end{tabular}};

  \caption{Distinguishing scenarios for sentence XYZ}
  \label{fig:EA-distinguishing-pics}
